\documentclass{article}
\usepackage{graphicx}
\usepackage{physics}
\usepackage{float}
\usepackage{amsfonts}
\title{Project 2 Report}
\author{Dreycen Foiles [dfoiles2] \\ Olek Yardas [yardsol]}
\date{\today}
\begin{document}
\maketitle

\section{Introduction}
In this assignment, we were tasked with predicting the weekly sales of
different departments at several Walmart stores using data from 45 different
stores in different regions.

\section{Data processing}
The data categories in the raw dataset are as follows: Store, Dept, Date,
Weekly\_Sales, IsHoliday. To generate the training data, test data, and extra
training folds, we first remove Date and replace it with two new categories:
Week and Year. We assigned a number from 1 to 52 for each week, and a number
from 1 to 3 for each year. These categories are much easier for a statistical model to interpret.

\section{Methods}
To do the regression, we initally tried using a GradientBoostedTree from
scikit-learn, but it did not perfrom very well. Next, we made a custom model
where we made a simple assumption that at a given department and store, there
was no variation year-over-year. More explicitly, we are assuming that the sales
at a given store at a given department would be the same as the same date 52
weeks ago. This method worked surprisingly well and, in our view, gave an excelletn cost-to-performance ratio.

\section{Results}

\begin{center}
    \begin{tabular}{|c|c|c|}
        \hline
        Fold & Runtime (s.) & WAE \\ 
        \hline \hline 
        1 & 0.171 & 2262.42 \\ 
        \hline
        2 & 0.169 & 177.08 \\ 
        \hline
        3 & 0.200 & 1779.05 \\ 
        \hline
        4 & 0.217 & 1716.12 \\ 
        \hline
        5 & 0.283 & 2400.40 \\ 
        \hline
        6 & 0.182 & 1696.90 \\ 
        \hline
        7 & 0.163 & 2086.96 \\ 
        \hline
        8 & 0.267 & 1750.28 \\ 
        \hline
        9 & 0.164 & 1719.89 \\ 
        \hline
        10 & 0.165 & 1680.96 \\ 
        \hline
        Avg & 0.203 & 1888.89 \\ 
        \hline 
    \end{tabular}
\end{center}


\section{Conclusion}

We struggled to get more robust models to successfully predict weekly sales. Unfortunately, our best model was not good enough to beat all the benchmarks. We attempted to fit a linear using weeks as features for each department in each store, but that was producing predictions that were very off. In this end, by far our best model was simply predicting that weekly sales would not change year-over-year. 


\end{document}
